---
title: "Clean"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Fix column missnaming
```{r}
data[[1]]%>%
	filter(!is.na(Country_Region));
```
Yes, there are some data that is formated incorectly

```{r}
data[[1]]=data[[1]]%>%
	mutate(
		`Country/Region`=if_else(
			is.na(
				Country_Region
			),
			`Country/Region`,
			Country_Region
		)%>%
			as.factor(),
		Country_Region=NULL,
		`Province/State`=if_else(
			is.na(
				Province_State
			),
			`Province/State`,
			Province_State
		)%>%
			as.factor(),
		Province_State=NULL,
		`Last Update`=if_else(
			is.na(
				Last_Update
			),
			`Last Update`,
			Last_Update
		),
		Last_Update=NULL,
		Combined_Key=NULL,
		Lat=if_else(
			is.na(
				Lat
			),
			Latitude,
			Lat
		),
		Latitude=NULL,
		Lon=if_else(
			is.na(
				Long_
			),
			Longitude,
			Long_
		),
		Longitude=NULL,
		Long_=NULL,
		Confirmed=as.integer(Confirmed),
		Deaths=as.integer(Deaths),
		Recovered=as.integer(Recovered)
	);
```


# Fix Last Update
```{r}
CSSEGIcountry=data[[1]]%>%
	filter(str_detect(`Last Update`,".*/.*"))%>%
	mutate(`Last Update`=lubridate::mdy_hm(`Last Update`));

CSSEGIcountry=data[[1]]%>%
	filter(str_detect(`Last Update`,".*-.*"))%>%
	mutate(`Last Update`=lubridate::ymd_hms(`Last Update`))%>%
	dplyr::union(CSSEGIcountry)%>%
	mutate(
		date=lubridate::as_date(`Last Update`)
	);
```

# Standardise data for US Data
```{r}
CSSEGIus=data[[2]]%>%
	mutate(
		Lon=Long_,
		Long_=NULL,
		`Province/State`=as.factor(Province_State),
		Province_State=NULL,
		`Country/Region`=as.factor(Country_Region),
		Country_Region=NULL,
		`Last Update`=Last_Update,
		Last_Update=NULL,
		date=lubridate::as_date(`Last Update`)
	);
```

# Add missing data
We need to predict each value that is unreported.  To do this let's plot them on a line graph.

```{r}
CSSEGIcountry%>%
	ggplot(aes(
		date,
		Confirmed,
		col=paste(`Province/State`, `Country/Region`)
	))+
	geom_point(show.legend=FALSE)+
	#geom_line(show.legend=FALSE)+
	geom_smooth(show.legend=FALSE, na.rm=TRUE, method=mgcv::gam, se=FALSE);
```

```{r}
predict=CSSEGIcountry%>%
	mutate(name=paste(`Province/State`, `Country/Region`))%>%
	group_by(name);

prdCon=predict%>%
	mgcv::gam(data=.,formula=Confirmed~date+name);

prdDea=predict%>%
	mgcv::gam(data=.,formula=Deaths~date+name);

prdRec=predict%>%
	mgcv::gam(data=.,formula=Recovered~date+name);
```

```{r}
predicted=mgcv::predict.gam(prdCon, predict);
```

That works, just need to merge the data.  We can use ids and join on them.


# Check for NAs

Is there any NAs?
```{r}
CSSEGIcountry%>%
	filter(is.na(Confirmed))
```
Not that many, but that does not show the true missing gaps.

Select the existing countries then cross join them with all the dates.
```{r}
courntry=CSSEGIcountry%>%
	select(`Province/State`, `Country/Region`)%>%
	unique();

date=CSSEGIcountry%>%
	select(date)%>%
	unique();

merge=courntry%>%
	mutate(k=1)%>%
	full_join(date%>%mutate(k=1), by='k')%>%
	select(-k);

all=merge%>%
	left_join(CSSEGIcountry, by=c("Province/State", "Country/Region", "date"));

all%>%
	filter(is.na(Confirmed));
```

There 35,322 missing opservations.  They should be predicted to fill in the gaps.