---
title: "Clean"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Fix column missnaming
```{r}
data[[1]]%>%
	filter(!is.na(Country_Region));
```
Yes, there are some data that is formated incorectly

```{r}
data[[1]]=data[[1]]%>%
	mutate(
		`Country/Region`=if_else(
			is.na(
				Country_Region
			),
			`Country/Region`,
			Country_Region
		)%>%
			as.factor(),
		Country_Region=NULL,
		`Province/State`=if_else(
			is.na(
				Province_State
			),
			`Province/State`,
			Province_State
		)%>%
			as.factor(),
		Province_State=NULL,
		`Last Update`=if_else(
			is.na(
				Last_Update
			),
			`Last Update`,
			Last_Update
		),
		Last_Update=NULL,
		Combined_Key=NULL,
		Lat=if_else(
			is.na(
				Lat
			),
			Latitude,
			Lat
		),
		Latitude=NULL,
		Lon=if_else(
			is.na(
				Long_
			),
			Longitude,
			Long_
		),
		Longitude=NULL,
		Long_=NULL,
		Confirmed=as.integer(Confirmed),
		Deaths=as.integer(Deaths),
		Recovered=as.integer(Recovered)
	);
```


# Fix Last Update
```{r}
CSSEGIcountry=data[[1]]%>%
	filter(str_detect(`Last Update`,".*/.*"))%>%
	mutate(`Last Update`=lubridate::mdy_hm(`Last Update`));

CSSEGIcountry=data[[1]]%>%
	filter(str_detect(`Last Update`,".*-.*"))%>%
	mutate(`Last Update`=lubridate::ymd_hms(`Last Update`))%>%
	dplyr::union(CSSEGIcountry)%>%
	mutate(
		date=lubridate::as_date(`Last Update`)
	);
```

# Standardise data for US Data
```{r}
CSSEGIus=data[[2]]%>%
	mutate(
		Lon=Long_,
		Long_=NULL,
		`Province/State`=as.factor(Province_State),
		Province_State=NULL,
		`Country/Region`=as.factor(Country_Region),
		Country_Region=NULL,
		`Last Update`=Last_Update,
		Last_Update=NULL,
		date=lubridate::as_date(`Last Update`)
	);
```

# Save data
As R keeps crashing, save the data.
```{r}
dir.create("data");
write_csv(CSSEGIcountry, "data/CSSEGIcountry.csv");
write_csv(CSSEGIus, "data/CSSEGIus.csv");
```

# Add missing data
We need to predict each value that is unreported.  To do this let's plot them on a line graph.

```{r}
CSSEGIcountry%>%
	ggplot(aes(
		date,
		Confirmed,
		col=paste(`Province/State`, `Country/Region`)
	))+
	geom_point(show.legend=FALSE)+
	#geom_line(show.legend=FALSE)+
	geom_smooth(show.legend=FALSE, na.rm=TRUE, method=mgcv::gam, se=FALSE);
```

### WARNING This takes a LONG time to generate and is not used in the long run

```{r}
predict=CSSEGIcountry%>%
	mutate(name=paste(`Province/State`, `Country/Region`))%>%
	group_by(name);

prdCon=predict%>%
	mgcv::gam(data=.,formula=Confirmed~date+name);

prdDea=predict%>%
	mgcv::gam(data=.,formula=Deaths~date+name);

prdRec=predict%>%
	mgcv::gam(data=.,formula=Recovered~date+name);
```

# Save the gam
This does not work and cannot load via `dget()`.
So instead save the image
```{r}
# dput(prdCon, file="data/prdCon.robj");
# dput(prdDea, file="data/prdDea.robj");
# dput(prdRec, file="data/prdRec.robj");

save.image("~/programming/R/SARS-CoV2/CSS.RData")
```
That is a lot of data, 32MB per file!

```{r eval=FALSE}
predicted=mgcv::predict.gam(prdCon, predict);
```

That works, just need to merge the data.  We can use ids and join on them.


# Check for NAs

Is there any NAs?
```{r}
CSSEGIcountry%>%
	filter(is.na(Confirmed))
```
Not that many, but that does not show the true missing gaps.

Select the existing countries then cross join them with all the dates.
```{r}
courntry=CSSEGIcountry%>%
	select(`Province/State`, `Country/Region`)%>%
	unique();

date=CSSEGIcountry%>%
	select(date)%>%
	unique();

merge=courntry%>%
	mutate(k=1)%>%
	full_join(date%>%mutate(k=1), by='k')%>%
	select(-k);

all=merge%>%
	left_join(CSSEGIcountry, by=c("Province/State", "Country/Region", "date"));

all%>%
	filter(is.na(Confirmed));
```

There 35,322 missing opservations.  They should be predicted to fill in the gaps.

# Fill the gaps
This takes way too long and does not work for the last two as there are missing predictions for some countries.  This should have been easy to fix, but I don't know how

Add index to all then pass all to `mgcv::predict.gam()`
```{r}
all=all%>%
	mutate(
		n=1:n(),
		name=paste(`Province/State`, `Country/Region`)
	);

con=prdCon%>%
	mgcv::predict.gam(all);

con=con%>%
	as_tibble()%>%
	mutate(n=1:n(), Confirmed=value, value=NULL);

# Issue with new levels
#dea=prdDea%>%
#	mgcv::predict.gam(all);

#dea=dea%>%
#	as_tibble()%>%
#	mutate(n=1:n());
#err
#rec=prdRec%>%
#	mgcv::predict.gam(all);

#rec=rec%>%
#	as_tibble()%>%
#	mutate(n=1:n());


all=all%>%
	inner_join(con, by='n', suffix=c('', '.prd'))#%>%
	#inner_join(dea, by='n', suffix=c('', '.prd'))%>%
	#inner_join(rec, by='n', suffix=c('', '.prd'));

all%>%
	mutate(
		prdConfirmed=is.na(Confirmed),
		Confirmed=ifelse(
			is.na(Confirmed),
			Confirmed.prd,
			Confirmed
		),
		Confirmed.prd=NULL#,
		
		
		#prdDeaths=is.na(Deaths),
		#Deaths=ifelse(
		#	is.na(Deaths),
		#	Deaths.prd,
		#	Deaths
		#),
		#Deaths.prd=NULL,
		#
		#prdRecovered=is.na(Recovered),
		#Recovered=ifelse(
		#	is.na(Recovered),
		#	Recovered.prd,
		#	Recovered
		#),
		#Recovered.prd=NULL
	);

write_csv(all, path="data/all.csv");
```