---
title: "Graph 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(plotly);
```

# WARNING THIS TAKES A LONG TIME TO RENDER (30 min to 60+ min)
# WARNING!!!!!  THIS PREVIOUSLY BLUE SCREENED MY COMPUTER!

```{r}
CSSEGIcountry%>%
	ggplot(aes(
		Confirmed,
		Recovered,
		size=Deaths,
		col=paste(`Country/Region`,`Province/State`),
		alpha=date
	))+
	geom_point(show.legend=FALSE)+
	geom_line(show.legend=FALSE, alpha=.2)+
	scale_x_log10()+
	scale_y_log10();
ggplotly();
```

Too much data, use time instead of alpha for date

This takes a while to generate, mainaly ggplotly.  Plus ggplotly lags R badly due to the size of the data.  Must use a popup, or it will not work well.
```{r eval=FALSE}
CSSEGIcountry%>%
	mutate(name=paste(`Country/Region`,`Province/State`))%>%
	ggplot(aes(
		Confirmed,
		Recovered,
		size=Deaths,
		col=name,
		frame=date
	))+
	geom_point(show.legend=FALSE)+
	scale_x_log10()+
	scale_y_log10();
plot=ggplotly();
# Widget is so large, save it as HTML when done
htmlwidgets::saveWidget(plot, "CSSEGIcountry2.html");
```

Too much data to use plotly.  plotly is too unoptomised to be used with this large of a data set.  It is just too laggy and unreliable to use and takes forever to render.  I need to find a different way to plot this data.


To remove invalid values add one
```{r}
CSSEGIcountry%>%
	ggplot(aes(
		Confirmed+1,
		Recovered+1,
		size=Deaths+1,
		col=paste(`Country/Region`,`Province/State`),
		alpha=date
	))+
	geom_point(show.legend=FALSE)+
	geom_line(show.legend=FALSE, alpha=.4)+
	scale_x_log10()+
	scale_y_log10();
```

There are still too much to see, remove the State data.

Does not work, thinks it's an `and`
```{r eval=FALSE}
CSSEGIpure=CSSEGIcountry%>%
	filter(
		is.na(`Province/State`)
		||
		`Province/State`==`Country/Region`
	);
```

```{r}
CSSEGIpure=CSSEGIcountry%>%
	filter(
		is.na(`Province/State`)
	)%>%
	dplyr::union(
		CSSEGIcountry%>%
			filter(
			# Fix factor issue
					as.character(`Province/State`)
				==
					as.character(`Country/Region`)
			)
	);
```

```{r}
CSSEGIpure%>%
	ggplot(aes(
		Confirmed+1,
		Recovered+1,
		size=Deaths,
		col=`Country/Region`,
		alpha=date
	))+
	geom_point(show.legend=FALSE)+
	geom_line(show.legend=FALSE, alpha=.4)+
	scale_x_log10()+
	scale_y_log10();
```

That was faster, let's see if plotly works now.  I honestly don't know if plotly cused my computer to crash or if it was somthing else.  The blue screen crash was `Unexpected Stop Code`, now I am conserned about the stability of this computer under this load.  Or it could just plotly causing the crash.  This project has been the most unstable project I have worked on period.  I am astonished that the computer actuaualy crashed while R was open and runing.  I do not know if it was working when the crash ocured, but I don't see anything else that could have caused it.

```{r}
CSSEGIpure%>%
	ggplot(aes(
		Confirmed+1,
		Recovered+1,
		size=Deaths,
		col=`Country/Region`,
		frame=date
	))+
	geom_point(show.legend=FALSE)+
	scale_x_log10()+
	scale_y_log10();
plot=ggplotly()%>%
  animation_opts(
    1000, easing = "elastic", redraw = FALSE
  );
htmlwidgets::saveWidget(plot, "CSSEGIpure.html")
```

That is not doing anything with time...

```{r}
CSSEGIpure%>%
	filter(`Country/Region`%in%c("US", "United Kingdom"))%>%
	ggplot()+
	geom_point(
		aes(
			Confirmed+1,
			Recovered+1,
			size=Deaths,
			col=`Country/Region`,
			frame=as.factor(date)
		)
	)+
	scale_x_log10()+
	scale_y_log10();
plot=ggplotly()
plot;
```

Turns out you need a factor!

```{r}
CSSEGIpure%>%
	ggplot(aes(
		Confirmed+1,
		Recovered+1,
		size=Deaths,
		col=`Country/Region`,
		id=`Country/Region`,
		frame=as.factor(date)
	))+
	geom_point(show.legend=FALSE)+
	scale_x_log10()+
	scale_y_log10();
plot=ggplotly();
htmlwidgets::saveWidget(plot, "CSSEGIpure.html")
```

Try it with all the data.

```{r}
CSSEGIcountry%>%
	ggplot(aes(
		Confirmed+1,
		Recovered+1,
		size=Deaths,
		col=paste(`Country/Region`,`Province/State`),
		frame=as.factor(date)
	))+
	geom_point(show.legend=FALSE)+
	scale_x_log10()+
	scale_y_log10();
plot=ggplotly();
htmlwidgets::saveWidget(plot, "CSSEGIcountry.html")
```
One issue is that the countries morph into eachother due to missing data.

3:26-4:24
```{r}
CSSEGIcountry%>%
	mutate(
		name=paste(`Country/Region`,`Province/State`),
		date=as.factor(date)
	)%>%
	ggplot(aes(
		Confirmed+1,
		Recovered+1,
		size=Deaths,
		col=name,
		id=name,
		frame=date
	))+
	geom_point(show.legend=FALSE)+
	scale_x_log10()+
	scale_y_log10();
plot=ggplotly();
htmlwidgets::saveWidget(plot, "CSSEGIcountry.html")
```

Now that I know this works let's try it again with the map data.

```{r eval=FALSE}
# Do a conditional join by a cross join and filter
# Cross jon is joining on a temporary column
cross=rnaturalearth::ne_countries(returnclass="sf")%>%
	mutate(k=1)%>%
	full_join(
		CSSEGIcountry%>%
			mutate(k=1),
		on='k'
	)%>%
	select(-k);
# Even this takes a while
cross%>%
	filter(
		
	);
```

```{r}
rnaturalearth::ne_countries(returnclass="sf")%>%
	as_tibble()
CSSEGIpure
```

That is taking too long, so instead inner_join multiple times and then union them.
```{r}
join=list();

join[[1]]=rnaturalearth::ne_countries(returnclass="sf")%>%
	inner_join(
		CSSEGIpure,
		by=c(name='Country/Region')
	)

join[[2]]=rnaturalearth::ne_countries(returnclass="sf")%>%
	inner_join(
		CSSEGIpure,
		by=c(name_long='Country/Region')
	)

join[[3]]=rnaturalearth::ne_countries(returnclass="sf")%>%
	inner_join(
		CSSEGIpure,
		by=c(brk_name='Country/Region')
	)

join[[4]]=rnaturalearth::ne_countries(returnclass="sf")%>%
	inner_join(
		CSSEGIpure,
		by=c(postal='Country/Region')
	)

join[[5]]=rnaturalearth::ne_countries(returnclass="sf")%>%
	inner_join(
		CSSEGIpure,
		by=c(abbrev='Country/Region')
	)

join[[6]]=rnaturalearth::ne_countries(returnclass="sf")%>%
	inner_join(
		CSSEGIpure,
		by=c(formal_en='Country/Region')
	)
```

```{r}
join[[1]]%>%
	dplyr::union(
		join[[2]]
	)

```

```{r}
test1=join[[1]]%>%
		head(1)%>%
		select(geometry);

test2=join[[2]]%>%
		head(1)%>%
		select(geometry);

dput(test1)%>%
	clipr::write_clip();

dput(test2)%>%
	clipr::write_clip();
```


```{r eval=FALSE}
library(tidyverse);
test1=list(list(c(61.2108170917257, 62.2306514830059, 62.9846623065766, 63.1935384459004, 63.9828959491587, 64.5464791197339, 64.7461051776774, 65.5889477883578, 65.7456307310668, 66.2173848814593, 66.5186068052887, 67.0757820982596, 67.8299996275595, 68.1355623717014, 68.8594458352459, 69.1962728209244, 69.518785434858, 70.1165784036103, 70.2705741718401, 70.3763041523093, 70.8068205097329, 71.3481311379903, 71.2394039244482, 71.5419177590848, 71.4486934752302, 71.8446382994506, 72.1930408059624, 72.6368896829173, 
73.260055779925, 73.9486959166465, 74.9800024758954, 75.1580277851409, 74.575892775373, 74.0675517109178, 72.9200248554445, 71.8462919452839, 71.2623482603857, 71.4987679381211, 71.6130762063507, 71.1150187519216, 71.1567733092135, 70.8818030129884, 69.9305432473596, 70.3235941913716, 69.6871472512649, 69.2625220071226, 69.3177641132426, 68.9266768736577, 68.5569320006093, 67.7926892434448, 67.6833935891475, 66.9388912291185, 66.381457553986, 66.3464726093244, 65.0468620136161, 64.3504187356185, 
64.1480021503313, 63.5502608580112, 62.5498568052728, 60.8742484882088, 61.7812215513634, 61.6993144061808, 60.9419446145111, 60.863654819589, 60.5360779152908, 60.963700392506, 60.5284298033116, 60.8031933938074, 61.2108170917257, 35.6500723333092, 35.2706639674223, 35.4040408391676, 35.8571656357189, 36.0079574651466, 36.3120732691843, 37.1118177353333, 37.3052167831856, 37.6611640488121, 37.3937901881339, 37.3627843287588, 37.3561439072093, 37.1449940048647, 37.0231151393043, 37.3443358424306, 
37.1511435003074, 37.6089966904134, 37.5882227646321, 37.735164699854, 38.1383959010275, 38.4862816432164, 38.2589053411322, 37.9532650823419, 37.9057744410656, 37.0656448430805, 36.7381712916469, 36.9482876653457, 37.0475580917784, 37.495256862939, 37.4215662704908, 37.4199901393059, 37.1330309107891, 37.0208413762835, 36.8361756454885, 36.7200070256963, 36.5099423284299, 36.0743875188578, 35.650563259416, 35.1532034368229, 34.7331257187222, 34.3489114446322, 33.9888559026385, 34.0201201441751, 
33.3585326197584, 33.1054989690412, 32.5019440780883, 31.9014122584244, 31.6201891138921, 31.713310044882, 31.5829304062096, 31.3031542017814, 31.3049112004794, 30.7388992375865, 29.8879434270362, 29.4721806910319, 29.5600306259281, 29.340819200146, 29.4683307968262, 29.3185724960443, 29.8292389999526, 30.7358503280812, 31.3795061304927, 31.5480746526288, 32.1829196233344, 32.9812688258116, 33.5288323023763, 33.676446031218, 34.4041018743199, 35.6500723333092)))

test2=list(list(c(61.2108170917257, 62.2306514830059, 62.9846623065766, 63.1935384459004, 63.9828959491587, 64.5464791197339, 64.7461051776774, 65.5889477883578, 65.7456307310668, 66.2173848814593, 66.5186068052887, 67.0757820982596, 67.8299996275595, 68.1355623717014, 68.8594458352459, 69.1962728209244, 69.518785434858, 70.1165784036103, 70.2705741718401, 70.3763041523093, 70.8068205097329, 71.3481311379903, 71.2394039244482, 71.5419177590848, 71.4486934752302, 71.8446382994506, 72.1930408059624, 72.6368896829173, 
73.260055779925, 73.9486959166465, 74.9800024758954, 75.1580277851409, 74.575892775373, 74.0675517109178, 72.9200248554445, 71.8462919452839, 71.2623482603857, 71.4987679381211, 71.6130762063507, 71.1150187519216, 71.1567733092135, 70.8818030129884, 69.9305432473596, 70.3235941913716, 69.6871472512649, 69.2625220071226, 69.3177641132426, 68.9266768736577, 68.5569320006093, 67.7926892434448, 67.6833935891475, 66.9388912291185, 66.381457553986, 66.3464726093244, 65.0468620136161, 64.3504187356185, 
64.1480021503313, 63.5502608580112, 62.5498568052728, 60.8742484882088, 61.7812215513634, 61.6993144061808, 60.9419446145111, 60.863654819589, 60.5360779152908, 60.963700392506, 60.5284298033116, 60.8031933938074, 61.2108170917257, 35.6500723333092, 35.2706639674223, 35.4040408391676, 35.8571656357189, 36.0079574651466, 36.3120732691843, 37.1118177353333, 37.3052167831856, 37.6611640488121, 37.3937901881339, 37.3627843287588, 37.3561439072093, 37.1449940048647, 37.0231151393043, 37.3443358424306, 
37.1511435003074, 37.6089966904134, 37.5882227646321, 37.735164699854, 38.1383959010275, 38.4862816432164, 38.2589053411322, 37.9532650823419, 37.9057744410656, 37.0656448430805, 36.7381712916469, 36.9482876653457, 37.0475580917784, 37.495256862939, 37.4215662704908, 37.4199901393059, 37.1330309107891, 37.0208413762835, 36.8361756454885, 36.7200070256963, 36.5099423284299, 36.0743875188578, 35.650563259416, 35.1532034368229, 34.7331257187222, 34.3489114446322, 33.9888559026385, 34.0201201441751, 
33.3585326197584, 33.1054989690412, 32.5019440780883, 31.9014122584244, 31.6201891138921, 31.713310044882, 31.5829304062096, 31.3031542017814, 31.3049112004794, 30.7388992375865, 29.8879434270362, 29.4721806910319, 29.5600306259281, 29.340819200146, 29.4683307968262, 29.3185724960443, 29.8292389999526, 30.7358503280812, 31.3795061304927, 31.5480746526288, 32.1829196233344, 32.9812688258116, 33.5288323023763, 33.676446031218, 34.4041018743199, 35.6500723333092)))


dplyr::union(test1, test2)
# This now works due to deserilization and lack of typing in dput
```

```{r}
library(tidyverse);
library(rnaturalearth);
rnaturalearth::ne_countries(returnclass="sf")%>%
	dplyr::union(
		ne_countries(returnclass="sf")
	)
```

# Replace geom with an ID to add it back latter

```{r}
join=list();

# Should be a tible so that dplyr works better
ne_co=rnaturalearth::ne_countries(returnclass="sf")%>%
	as_tibble()%>%
	mutate(id=1:n());

ne_geo=ne_co%>%
	select(id, geometry);

ne_co=ne_co%>%
	select(-geometry);

join[[1]]=ne_co%>%
	inner_join(
		CSSEGIpure,
		by=c(name='Country/Region')
	)

join[[2]]=ne_co%>%
	inner_join(
		CSSEGIpure,
		by=c(name_long='Country/Region')
	)

join[[3]]=ne_co%>%
	inner_join(
		CSSEGIpure,
		by=c(brk_name='Country/Region')
	)

join[[4]]=ne_co%>%
	inner_join(
		CSSEGIpure,
		by=c(postal='Country/Region')
	)

join[[5]]=ne_co%>%
	inner_join(
		CSSEGIpure,
		by=c(abbrev='Country/Region')
	)

join[[6]]=ne_co%>%
	inner_join(
		CSSEGIpure,
		by=c(formal_en='Country/Region')
	)
```


```{r}
join=join[[1]]%>%
	dplyr::union(join[[2]])%>%
	dplyr::union(join[[3]])%>%
	dplyr::union(join[[4]])%>%
	dplyr::union(join[[5]])%>%
	dplyr::union(join[[6]]);

join=join%>%
	inner_join(ne_geo, by="id")%>%
	select(-id);
```
That worked fine!
May need to convrt back to an sf object

# Now we can try to graph it

This will likely take longer than the pervious graph as it has more data to deal with.

### NOTE: This does not end up to work, the wiget is too laggy and even crashed mozzila.

```{r}
join%>%
	select(name,Confirmed,date,geometry)%>%
	mutate(
		name=as.factor(name),
		date=as.factor(date)
	)%>%
	ggplot(aes(
		fill=Confirmed,
		id=name,
		frame=date,
		geometry=geometry
	))+
	geom_sf();
plot=ggplotly();
htmlwidgets::saveWidget(plot, "CSSEGImap.html")
```

This works, but in HTML it lages soo much!  It is imposible to see what is going on.  It is a shame.  I had to close Firefox because of this wiget.  Good thing I though of using a second browser.

Lets see if changing the options helps it
```{r}
plot%>%
	animation_opts(
		redraw=FALSE
	);
htmlwidgets::saveWidget(plot, "CSSEGImap2.html")
```

I don't even know if it is better, it still takes a long time to animate.  So it turns out that ggplotly is a bad way to aminate sf graphs.